Individual and Differential Harm in Redistricting

### 2023-07-14 paper/harm-short.Rmd
title page

---
title: Individual and Differential Harm in Redistricting
authors:
  - name: Cory McCartan
    thanks: |
      To whom correspondence should be addressed.
      The authors thank Steve Ansolabehere, Matt Blackwell, Kosuke Imai, Gary King, 
      Shiro Kuriwaki, Tyler Simko, Nick Stephanopolous, and 
      participants of the Fall 2021 Harvard American Politics Research Workshop,
      Fall 2022 Harvard Applied Statistics Workshop, 
      and Imai Research Group for helpful comments and discussion.
      Replication code and data are available at <https://github.com/CoryMcCartan/harm-redistricting>.
    department: Faculty Fellow, Center for Data Science
    affiliation: New York University
    location: 60 5th Ave, New York, NY
    email: corymccartan@nyu.edu
  - name: Christopher T. Kenny
    department: Ph.D. Candidate, Department of Government
    affiliation: Harvard University
    location: 1737 Cambridge St., Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Social scientists have developed dozens of measures for assessing partisan bias in redistricting.
  But these measures are not easily adapted to other groups, 
  including groups defined by race, class, or geography.
  Nor are they applicable to single- or no-party contexts, such as local redistricting.
  To overcome these limitations, we propose a unified framework of harm for evaluating 
  the impacts of a districting plan on individual voters and the groups to which they belong. 
  We consider a voter harmed if their chosen candidate is not elected under the current plan, 
  but would be under a different plan.
  Harm improves on existing measures by both focusing on the choices of individual voters 
  and directly incorporating counterfactual plans.
  We discuss strategies for estimating harm, and demonstrate the utility of our framework 
  through analyses of partisan gerrymandering in New Jersey and voting rights 
  litigation in Alabama.
keywords:
  - representation
  - redistricting
  - voting rights
  - individual harm
bibliography: references.bib
biblio-style: apsr
fontsize: 12pt
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
editor_options:
  markdown:
    wrap: sentence
---

@@

\begin{center}\bfseries 9,970 words\end{center}

>>>>

---
title: Individual and Differential Harm in Redistricting
# authors:
#   - name: Cory McCartan
#     thanks: |
#       To whom correspondence should be addressed.
#       The authors thank Steve Ansolabehere, Matt Blackwell, Kosuke Imai, Gary King, 
#       Shiro Kuriwaki, Tyler Simko, Nick Stephanopolous, and 
#       participants of the Fall 2021 Harvard American Politics Research Workshop,
#       Fall 2022 Harvard Applied Statistics Workshop, 
#       and Imai Research Group for helpful comments and discussion.
#       Replication code and data are available at <https://github.com/CoryMcCartan/harm-redistricting>.
#     department: Faculty Fellow, Center for Data Science
#     affiliation: New York University
#     location: 60 5th Ave, New York, NY
#     email: corymccartan@nyu.edu
#   - name: Christopher T. Kenny
#     department: Ph.D. Candidate, Department of Government
#     affiliation: Harvard University
#     location: 1737 Cambridge St., Cambridge, MA
#     email: christopherkenny@fas.harvard.edu
abstract: |
  Social scientists have developed dozens of measures for assessing partisan bias in redistricting.
  But these measures are not easily adapted to other groups, 
  including groups defined by race, class, or geography.
  Nor are they applicable to single- or no-party contexts, such as local redistricting.
  To overcome these limitations, we propose a unified framework of harm for evaluating 
  the impacts of a districting plan on individual voters and the groups to which they belong. 
  We consider a voter harmed if their chosen candidate is not elected under the current plan, 
  but would be under a different plan.
  Harm improves on existing measures by both focusing on the choices of individual voters 
  and directly incorporating counterfactual plans.
  We discuss strategies for estimating harm, and demonstrate the utility of our framework 
  through analyses of partisan gerrymandering in New Jersey and voting rights 
  litigation in Alabama.
keywords:
  - representation
  - redistricting
  - voting rights
  - individual harm
bibliography: references.bib
biblio-style: apsr
fontsize: 12pt
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
editor_options:
  markdown:
    wrap: sentence
---

@@

\begin{center}\bfseries 9,970 words\end{center}
\clearpage
